---
output:
  flexdashboard::flex_dashboard:
    source_code: "https://github.com/montilab/Xposome/"
    orientation: rows
    vertical_layout: fill
    css:
    - www/style.css
    - www/docsearch.css
    - www/bootstrap-toc.css
---

```{r packages}

library(flexdashboard)
library(rmarkdown)
library(badger)
library(knitr)
library(shiny)
library(shinyjs)

version= "0.0.1"

my_title <- paste0("<span><a class='navbar-link' href='#home'><strong>Xposome</strong></a>&ensp;<span class='version-label label-default' data-toggle='tooltip' data-placement='bottom' title='Released version'>", version, "</span></span>")

```

<script type="text/javascript">
  document.querySelector(".navbar-header > span.navbar-brand").innerHTML = "`r my_title`";

  $(document).ready(function() {
    document.title = "Xposome";
  });
  
  function ToggleOperation(id) {
    var x = document.getElementById(id+"-block");
    if (x.style.display === "none") {
      x.style.display = "block";
    } else {
      x.style.display = "none";
    }
  }
</script>


Home {data-icon="fa-home"}
=====================================

```{r mainpage}
fluidRow(
  column(
    width=8,
    includeMarkdown("home/home.Rmd")
  ),
  column(
    width=3, offset=1, id="pkgdown-sidebar",
    includeMarkdown("links.Rmd")
  ),
  column(
    width=12,
    includeMarkdown("footer.Rmd")
  )
)

```

NGINX and Docker-Compose {data-icon="fa-plug"}
=====================================  

```{r docker-compose}

fluidRow(
  column(
    width=8,
    includeMarkdown("docker-compose/docker-compose.Rmd")
  ),
  column(
    width=3, offset=1, id="pkgdown-sidebar",
    includeMarkdown("links.Rmd")
  ),
  column(
    width=12,
    includeMarkdown("footer.Rmd")
  )
)

```

Send Emails with Postfix {data-icon="fa-envelope-square"}
=====================================  

```{r postfix}

fluidRow(
  column(
    width=8,
    includeMarkdown("postfix/postfix.Rmd")
  ),
  column(
    width=3, offset=1, id="pkgdown-sidebar",
    includeMarkdown("links.Rmd")
  ),
  column(
    width=12,
    includeMarkdown("footer.Rmd")
  )
)

```

API Explorer {data-icon="fa-link"}
=====================================

```{r api}

fluidRow(
  column(
    width=8,
    includeMarkdown("api/api.Rmd")
  ),
  column(
    width=3, offset=1, id="pkgdown-sidebar",
    includeMarkdown("links.Rmd")
  ),
  column(
    width=12,
    includeMarkdown("footer.Rmd")
  )
)

```
